|

### 2023-03-10 paper/00-main.Rmd
TAS template

---
title: |
  Introducing STRAIN: A simple and interpretable pass rush metric inspired by materials science
short_title: STRAIN
authors: 
- name: "Author1"
  affiliation: "Address"
  city: "City"
  country: "Country"
  email: "email1\\@example.com"
- name: "Author2"
  affiliation: "Address2"
  city: "City2"
  country: "Country2"
  email: "email2\\@example.com"
- name: "Author3"
  affiliation: "Address3"
  city: "City3"
  country: "Country3"
  email: "email3\\@example.com"
abstract: |
  Abstract goes here
keywords: tracking data, Bornn legacy, too much Canadian
header-includes:
  \usepackage{booktabs}
output: rticles::rss_article
bibliography: bibliography.bib
---

>>>>

---
title: |
  STRAIN: A Continuous-Time Within-Play Statistic for Evaluating Pass Rush in American Football with Tracking Data

# to produce blinded version set to 1
blinded: 0

authors: 
- name: Quang Nguyen
  # thanks: uncomment to add corresponding author's email
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Ronald Yurko
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: |
    | Department of Mathematics and Statistics
    | Loyola University Chicago

keywords:
- tracking data
- football
- pass rush
- statistics in sports

abstract: |
  The text of your abstract.  200 or fewer words.

bibliography: bibliography.bib
output: rticles::asa_article
---

### 2023-03-10 paper/01-introduction.Rmd
TAS template

---
output: rticles::rss_article
bibliography: bibliography.bib
---

@@

\begin{table}
\caption{A summary of previously-existed pass rush metrics. \label{tab:metrics}}
\centering
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Description}\\
\midrule
Sacks & a\\
Hits & a\\
Hurries & a\\
QB Pressures & a\\
Pass-Rush Productivity (PRP) & a\\
Time In Pocket (TIP) & a\\
Pass Rush Win Rate (PRWR) & Rate at which pass rusher beats pass block within 2.5 seconds after snap\\
\bottomrule
\end{tabular}
\end{table}

>>>>

---
bibliography: bibliography.bib
output: rticles::asa_article
---

@@

\begin{table}
\caption{A summary of previously-existed pass rush metrics. \label{tab:metrics}}
\begin{center}
\begin{tabular}{ll}
\textbf{Metric} & \textbf{Description}\\\hline
Sacks & a\\
Hits & a\\
Hurries & a\\
QB Pressures & a\\
Pass-Rush Productivity (PRP) & a\\
Time In Pocket (TIP) & a\\
Pass Rush Win Rate (PRWR) & Rate at which pass rusher beats pass block within 2.5 seconds after snap\\\hline
\end{tabular}
\end{center}
\end{table}
